The database$^{[1]}$ is divided into many tables. Out of these tables, the tables we can currently get information from (and their columns) are:

\begin{enumerate}

\item \verb`patent`: This table contains primary information about the patent. 
\begin{enumerate} 
\item title: The Title of the Patent
\item id: The patent ID. This is a unique number for each patent.
\item date: The date on which this patent was issued. 
\item country: The country where this patent was issued.
\end{enumerate}

\item \verb`rawinventor`: This table contains information about the patent’s inventor.
\begin{enumerate}
\item name\_first: The first name of the inventor.
\item name\_last: The last name of the inventor.
\item nationality: The nationality of the inventor.
\item location\_id: Column to establish a relationship between inventors and locations. This contains the id of the location of the inventor.
\item patent\_id: Column to establish a relationship between a patent and its inventor. This contains the id of the patent to which it refers to.
\end{enumerate}

\item \verb`rawassignee`: This table contains information about the entity that assigned this patent.
\begin{enumerate}
\item name\_first: The first name of the assignee.
\item name\_last: The last name of the assignee.
\item nationality: The nationality of the assignee.
organization: Name of the organization this assignee belongs to (if any).
\item location\_id: Column to establish a relationship between inventors and locations. This contains the id of the location of the assignee.
\item patent\_id: Column to establish a relationship between a patent and its assignee. This contains the id of the patent to which it refers to.
\end{enumerate}

\item \verb`rawlawyer`: 
\begin{enumerate}
\item name\_first: The first name of the inventor.
\item name\_last: The last name of the inventor.
\item organization: Name of the organization this assignee belongs to (if any).
\item country: Country where the lawyer (organization) exists.
\item patent\_id: Column to establish a relationship between a patent and its lawyer. This contains the id of the patent to which it refers to.
\end{enumerate}

\item \verb`rawlocation`: This table stores information for different locations.
\begin{enumerate}
\item id: Unique number for each location.
\item city: The name of the city.
\item state: The name of the state.
\item country: The name of the country.
\end{enumerate}

\item \verb`claim`: This table stores information about the claims of every patent.
\begin{enumerate}
\item patent\_id: Column to establish a relationship between a patent and its lawyer. This contains the id of the patent to which the claim refers to.
\item text: The text of this claim.
\item dependent: ID of the claim this claim is dependent on.
\item sequence: ID of this claim.
\end{enumerate}

\item \verb`uspatentcitation`: This table stores information on all the citations in a patent.
\begin{enumerate}
\item patent\_id: Column to establish a relationship between a patent and its lawyer. This contains the id of the patent to which it refers to.
\item date: The date this citation was made.
\item country: The country in which this citation was made.
\item sequence: The ID of the citation.
\end{enumerate}


\end{enumerate}